\plaintitle

### 2016-09-08 drafts/labor/flexibility.tex
'closing' slicing.tex for now, moving on to flexibility

\ali{TODO:
\begin{enumerate}
  \item segue
  \item \crowdworkpers
  \item \pieceworkpers
  \item \whatchanged
\end{enumerate}
}

A number of researchers have identified
worker attrition,
variability of worker performance,
and uncertainty about good versus bad--faith actors as open questions of crowdwork
\cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
\ali{We can and should discuss the distinction between presumably ``bad faith'' workers
\& workers who are merely responding in kind to bad requesters
--- and the broader questions surrounding
the roles that requesters as well as workers should play ---
but let it suffice to say that
requesters have been trying to understand and manage what appears to them as inconsistent work.
Their ways of responding to that variance in work quality has largely involved
making the work more flexible and resilient to work
(although some work has gone into investigating the causes, rather than treating the symptoms)}

@@

\onlyinsubfile{
  % \balance{}
  % \printbibliography
}

>>>>

\ali{TODO:
\begin{enumerate}
  \item \crowdworkpers
  \item \pieceworkpers
  \item \whatchanged
\end{enumerate}
}

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  % \nobalance{}

  \begin{appendices}
  A number of researchers have identified
  worker attrition,
  variability of worker performance,
  and uncertainty about good versus bad--faith actors as open questions of crowdwork
  \cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
  \ali{We can and should discuss the distinction between presumably ``bad faith'' workers
  \& workers who are merely responding in kind to bad requesters
  --- and the broader questions surrounding
  the roles that requesters as well as workers should play ---
  but let it suffice to say that
  requesters have been trying to understand and manage what appears to them as inconsistent work.
  Their ways of responding to that variance in work quality has largely involved
  making the work more flexible and resilient to work
  (although some work has gone into investigating the causes, rather than treating the symptoms)}

@@

\end{appendices}
}

### 2016-09-08 drafts/labor/slicing.tex
'closing' slicing.tex for now, moving on to flexibility

\subsubsubsection{\pieceworkpers}
The beginnings of systematized task decomposition stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to \textit{compute} astronomical phenomena
\cite{grier2013computers}.
Airy's tasks were unique at the time for several reasons:
\begin{enumerate}
  \item Each task was quickly verifiable by a qualified (human) computer;
  \item tasks were discrete --- that is, independent from one another; and
  \item knowledge of the full scope of the project
  --- indeed, knowledge of anything more than the problem set at hand ---
  was unnecessary.
\end{enumerate}

\subsubsubsection{\whatchanged}
\ali{todo}

\onlyinsubfile{
  \balance{}
  \printbibliography

>>>>

\subsubsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute, by hand, astronomical phenomena
\cite{grier2013computers}.
These workers became the first \textit{computers}.

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
\ali{I could point out that the opportunity to check work and
repeat the task is a little like find--fix--verify, but is that jumping the gun?}
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

The insight of breaking tasks down into smaller components didn't find its audience until
the early \nth{20} century,
with the rise of Fordism and scientific management (or Taylorism).
From scientific management, we found that
we could measure work at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers, but certainly
in Ford and Taylor's time --- and certainly in Airy's time ---
highly instrumented, automatic measurement of workers was all but impossible.
As a result,
the distillation of work into smaller chunks
ultimately reached a limit of usefulness.

\ali{\citeauthor{marx2012economic} in here? Alienated from the context of the work?
Critiques about piecework marginalizing workers?
\citeauthor{american1921problem} wrote about this as well
(albeit they were advocating from workers' perspectives, but who isn't?)}

\subsubsubsection{\whatchanged}
\begin{inlinelist}
  \item Computers make it possible to switch from one task to another
  unlike any arbitrary manufacturing factory possibly could;
  \item we've sliced works to such small sizes that the marginal costs
  --- things like task--finding, cognitive load switching, etc\dots ---
  have become relatively large;
  \item instrumentation has become so advanced that
  the curve of diminishing value on measuring and tracking workers has shifted significantly
  (but not been obliterated);
  \ali{some companies have suggested self--tracking through
  programs that give workers fitbits and whatnot --- I could make the argument that
  this is just an illustration of that, but
  it's not really about work \textit{per se} unless
  you think about it as the general management of workers. Thoughts?}
\end{inlinelist}

\onlyinsubfile{
  % \balance{}
  \printbibliography

### 2016-09-08 drafts/theoryPaper/proceedings.tex
various intro revs
'closing' slicing.tex for now, moving on to flexibility

\documentclass{sigchi}
\usepackage{graphics,balance,txfonts,mathptmx,color,booktabs,color,booktabs,textcomp,microtype,ccicons}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}
\def\plaintitle{Laying Groundwork For a Worker--Centric Peer Economy}
\def\plainauthor{Ali Alkhatib, Justin Cranshaw, Andrés Monroy-Hernandez}
\def\emptyauthor{Anonymous for Review}
\def\plainkeywords{Peer economy; Collaborative markets}
\def\plaingeneralterms{Documentation, Standardization}

@@

\numberofauthors{4}
\author{
  \alignauthor{Ali Alkhatib                 \affaddr{Stanford University}   \affaddr{Stanford, USA}
        \email{ali.alkhatib@cs.stanford.edu}}
  \alignauthor{Justin Cranshaw              \affaddr{Microsoft Research}    \affaddr{Redmond, WA, USA}
        \email{justincr@microsoft.com}}
  \alignauthor{Andrés Monroy-Hernandez      \affaddr{Microsoft Research}    \affaddr{Redmond, WA, USA}
        \email{amh@microsoft.com}}
  \alignauthor{Michael Bernstein      \affaddr{Stanford University}    \affaddr{Stanford, USA}
        \email{msb@cs.stanford.edu}}
}
\numberofauthors{1} \author{ \alignauthor{\emptyauthor} }
\maketitle

\begin{abstract}
The ``gig economy''
--- where work is measured through discrete tasks rather than through interconnected (and often long--running) careers ---
has become a site of significant frustration among workers who have come to rely on these systems and this form of work.
This paper explores some of the sources of that stress,
and attempts to relate this seemingly nascent work style to more familiar forms of labor
--- namely, ``piece work'',
a form of work which emerged at the dawn of the 20th century.
While we find and identify parallels between ``gig work'' and the more theoretically familiar ``piece work'',
we emphasize divergences which make the conflation of these ideas problematic.

We further explore opportunities and tactics to empower workers,
informed by ethnographic fieldwork including participant--observation,
semi--structured interviews,
and participatory design.
Our observation and interviews lead us to conclude that the most intuitive mechanisms for empowering workers
--- namely, labor unions advocating collectively and counter--balancing the manager's outsize leverage ---
may both structurally and culturally fail to capture the needs of ``gig workers''.
We argue that design interventions to empower ``gig workers'' must build on the theoretically familiar,
much as ``gig work'' itself draws inspiration from ``piece work'',
but that it is crucial that interventions are designed to support,
rather than reject,
the unique cultural and system qualities of gig workers.
\end{abstract}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

\keywords{\plainkeywords}

\section*{Dealing with Monopsonies}
\section*{Collective Bargaining}

% \input{intro.tex}
% \input{background.tex}
% \input{fieldwork_advice.tex}
% \input{design_guidance.tex}
% \input{discussion.tex}

% % REFERENCES FORMAT
% % References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{../references}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass{sigchi}
\usepackage{graphics,balance,txfonts,mathptmx,color,booktabs,color,booktabs,textcomp,microtype,ccicons}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}
\def\plaintitle{Here's a title!}
\def\plainauthor{People here!}
\def\emptyauthor{Anonymous for Review}
\def\plainkeywords{???????????}
\def\plaingeneralterms{????}

@@

\numberofauthors{1}
\author{
    \alignauthor{Kenji Hata, Ranjay Krishna, Li Fei--Fei, Michael S. Bernstein}\\
    \affaddr{Stanford University}\\
    \email{\{kenjihata, ranjaykrishna, feifeili, msb\}@cs.stanford.edu}
  }
\maketitle
\end{document}

% \begin{abstract}
% The ``gig economy''
% --- where work is measured through discrete tasks rather than through interconnected (and often long--running) careers ---
% has become a site of significant frustration among workers who have come to rely on these systems and this form of work.
% This paper explores some of the sources of that stress,
% and attempts to relate this seemingly nascent work style to more familiar forms of labor
% --- namely, ``piece work'',
% a form of work which emerged at the dawn of the 20th century.
% While we find and identify parallels between ``gig work'' and the more theoretically familiar ``piece work'',
% we emphasize divergences which make the conflation of these ideas problematic.

% We further explore opportunities and tactics to empower workers,
% informed by ethnographic fieldwork including participant--observation,
% semi--structured interviews,
% and participatory design.
% Our observation and interviews lead us to conclude that the most intuitive mechanisms for empowering workers
% --- namely, labor unions advocating collectively and counter--balancing the manager's outsize leverage ---
% may both structurally and culturally fail to capture the needs of ``gig workers''.
% We argue that design interventions to empower ``gig workers'' must build on the theoretically familiar,
% much as ``gig work'' itself draws inspiration from ``piece work'',
% but that it is crucial that interventions are designed to support,
% rather than reject,
% the unique cultural and system qualities of gig workers.
% \end{abstract}

% \category{H.5.m.}{Information Interfaces and Presentation
%   (e.g. HCI)}{Miscellaneous} \category{See
%   \url{http://acm.org/about/class/1998/} for the full list of ACM
%   classifiers. This section is required.}{}{}

% \keywords{\plainkeywords}

% \section*{Dealing with Monopsonies}
% \section*{Collective Bargaining}

% % \input{intro.tex}
% % \input{background.tex}
% % \input{fieldwork_advice.tex}
% % \input{design_guidance.tex}
% % \input{discussion.tex}

% % % REFERENCES FORMAT
% % % References must be the same font size as other body text.
% \bibliographystyle{SIGCHI-Reference-Format}
% \bibliography{references}

% \end{document}

% %%% Local Variables:
% %%% mode: latex
% %%% TeX-master: t
% %%% End:
